\lecture{1}{jeu 13 fev 2020}
\vspace{-1.2cm}

\section{Digital challenging our world}

The world has changed and digital has profoundly changed our lives.

Example 1: campaign to get people to download a fast food app
The whooper detour
Whooper for 1 penny by using the app close to a McDonalds
App moved from a very low ranking to 1st in App Stores

(Example from teacher's experience: with facebook you can geotarget so precisely. He had an italian drinks client, targetted users that were in bars/restaurants that are "italian inspired" to give them a free drink)

Example 2: Facebook rules against female nudity. campaign of MACMA (Movimiento ayuda cancer de Mama). Used male breasts to show how to test for breast cancer.

Example 3: Fashion VS environnment.
Digital Virtual Collection. Clothes worn only on digital space.
3D modelling and OCR to fit clothes on existing photo of people.
CARLINGS (brand).

Example 4: Wendy's
Fortnite. Burger VS pizza movement. Wendy's destroyed burger freezers.
Huge Twitch movement. Utiliser plus de touchpoints tout en respectant les règles de tous les touchpoints


DATA is EVERYWHERE (lol)
It is the new currency of our economy

Super Bowl stats and Pornhub
MASSIVE investment of money
Stats to check the drop in activity during Super Bowl.

MF ELON MUSK launching a effing car in space.

The consummer has changed
TV has changed too (see Netflix bandersnatch and SKAM)
Netflix and Facebook are starting to eat TV's space (e.g. livestreams of sport)

Shark fin Adoption Curve
Big Bang Market Segments
Innovators - Early adopters - Early Majority - Late Majority - Laggards
The curve has moved from a Bell Curve to a Shark Fin curve
Massive bump in the Early adopters and Early Majority

Companys whose central market is something they don't have/make
e.g. Uber has no cars, Facebook produces no media, Alibaba has no inventory, Airbnb has no real estate.

Most valuable companies in the world have shifted to digital companies.

Digital companies in the context of industrial (something)
First industrial revolution: 1784 Mechanization, steam power, weaving loom
Second industrial revolution: 1800s Electricity
Third : 1990s Computing
Fourth: Today "Intelligence" (AI, 3d printing, robotics, autonomous vehicles, IoT, quantum computing)

(see CNBC show)
Klaus Schwab - Coined the term 4th industrial revolution
Technology merging with people's lives
Technology gets 100M adopters a LOT faster
Patents have grown exponentially

The big four > Microsoft IBM Cisco Intel
GAFA > Google Apple Facebook Amazon
NATU > Netflix Airbnb Tesla Uber

Setting the standards in terms of usage and technology
Google : winning the broser war in 4 years
Apple: creating the tablet market in 80 days
Facebook: capturing 16percent of your time in 10 years
Amazon: replacing your favorite grocer in 7 years

Companies are disrupting all industries

Google and Facebook business model
30pourcent de la population mondiale
Facebook's 10 year challenge. What's behind it? Face-recognition data.
Organic reach lowering from 100 percent to 50percent to now not even 10.
Big profits and small paybaks: most of them are avoiding takes

Conversion rate = purchase / clicks on adverts

Uberization
The same market is transformed by a challenger adapting generation
Phénomène récent services permettant aux professionels et aux clients de se mettre en contact direct.

Telslaization
Knowledge in a technology that will completely change another market
